Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

Recall the definition of the Shannon entropy:
\begin{align*}
	H(F) = -\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx.
\end{align*}
This can be written as
$$
H(F) = \int_{0}^{1} \ln \Big( \frac{d}{dy} F^{-1}(y) \Big) \, dy.
$$
See the proof in the Appendix.

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F$ by the empirical cumulative distribution function,
	\item approximate the derivative with finite differences (called ``spacings''),
	\item approximate the integral with a summation.
\end{itemize}

@@

However, we will use an improved bootstrap-improved
version $\widetilde{H}_{\text{AO}}(\bm Z)$ because it performs better with small samples.
See details in \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics}.
\end{frame}

>>>>

Recall the definition of the Shannon entropy:
\begin{equation*}
	H(F) = -\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx.
\end{equation*}

We want an estimator for $H(F)$, for example
$$
\widehat{H}(F) = H(\widehat{F}) = -\int_{-\infty}^\infty \widehat{f}(x) \ln\big(\widehat{f}(x)\big) dx,
$$
but how will we estimate $f$?

Two ways to estimate $f$:
\begin{itemize}
	\item estimating the parameters $\widehat{f}(x;\bm\theta) = f(x;\widehat{\bm \theta})$,
	\item estimating the density in a non-parametric way.
\end{itemize}

Parameter estimation $f(x;\widehat{\bm \theta})$ is \alert{inadequate}, because we are not sure which is the best model.

Density estimation $\widehat{f}$ is \alert{tricky} because we want to work with small samples.

\framebreak

The Shannon entropy can be written as
$$
H(F) = 
-\int_{-\infty}^\infty f(x) \ln\big(f(x)\big) dx =
\int_{0}^{1} \ln \Big( \frac{d}{dy} F^{-1}(y) \Big) \, dy.
$$
See the proof in the Appendix.

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F$ by the empirical cumulative distribution function,
	\item its inverse, the quantile function $F^{-1}$, by the order statistics
	\item approximate the derivative with finite differences (called ``spacings''),
	\item approximate the integral with a summation.
\end{itemize}

@@

However, we will use a bootstrap-improved
version $\widetilde{H}_{\text{AO}}(\bm Z)$ because it performs better with small samples.
See details in \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics}.
\end{frame}
